% !TEX root = ../resume.tex
%-------------------------------------------------------------------------------
% SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Extracurricular Activities}

%-------------------------------------------------------------------------------
% CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Aarhus University} % Organization/group
    {PhD Student (Period Abroad)} % Affiliation/role
    {Aarhus, Denmark} % Location
    {Aug. 2022 - Nov. 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Focused on studying advanced techniques in many-agent reinforcement learning, applied within the context of tracking spatio-temporal phenomena using graph neural networks.}
      \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
    {University of Bologna} % Organization/group
    {Presenter and Educator} % Affiliation/role
    {Cesena, Italy} % Location
    {Aug. 2021 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Conducted seminars on multi-agent reinforcement learning, large language models in software engineering, advanced functional programming, and advanced Scala features. Slides and resources are available in my GitHub repository.}
      \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
    {Various International Conferences} % Organization/group
    {Volunteer} % Affiliation/role
    {} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Volunteered at several international conferences during my PhD, including ACSOS 2022 and ICDCS 2022, assisting in organizational and technical support roles.}
      \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
    {Academic Journals and Conferences} % Organization/group
    {Reviewer Activities} % Affiliation/role
    {} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Served as a reviewer for various journals (e.g., Frontiers in Robotics, Science of Computer Programming) and international conferences (e.g., AAMAS, ACSOS, COORDINATION, ASE NIER, PerCom) during my PhD.}
      \end{cvitems}
    }
%---------------------------------------------------------
\end{cventries}
